Assessing Lime

### 2019-08-24 journals/03-applying_lime_logistic/03-applying_lime_logistic.Rmd
updated journals after organization

  # Save the model
  saveRDS(logistic_mains, "./data/logistic_mains.rds")

@@

  # Load the model
  logistic_mains <- readRDS("./data/logistic_mains.rds")

@@

```{r}
# Fit or load the logistic regression model with all two way interactions
if(!file.exists("./data/logistic_inters2.rds")) {

@@

  # Save the model
  saveRDS(logistic_inters2, "./data/logistic_inters2.rds")

@@

  # Load the model
  logistic_inters2 <- readRDS("./data/logistic_inters2.rds")

@@

```{r}
# Fit or load the lasso logistic regression model
if(!file.exists("./data/logistic_lasso.rds")) {

@@

  # Save the model
  saveRDS(logistic_lasso, "./data/logistic_lasso.rds")

@@

  # Load the model
  logistic_lasso <- readRDS("./data/logistic_lasso.rds")

@@

```{r}
# Create or load the lime and explain objects for the main effects logisitic regression model
if(!file.exists("./data/lime_explain_mains.rds")) {

@@

  # Save the lime and explain objects
  saveRDS(lime_explain_mains, "./data/lime_explain_mains.rds")

@@

  # Load the lime and explain objects
  lime_explain_mains <- readRDS("./data/lime_explain_mains.rds")

@@

```{r}
# Apply the run_lime function if the lime results file does not already exist
if(!file.exists("./data/logistic_lime_inputs.rds")) {

@@

  # Save the lime objects
  saveRDS(logistic_lime_inputs, "./data/logistic_lime_inputs.rds")
  saveRDS(logistic_lime, "./data/logistic_lime.rds")
  saveRDS(logistic_explain, "./data/logistic_explain.rds")

@@

  # Load in the lime objects
  logistic_lime_inputs <- readRDS("./data/logistic_lime_inputs.rds")
  logistic_lime <- readRDS("./data/logistic_lime.rds")
  logistic_explain <- readRDS("./data/logistic_explain.rds")

@@

```{r}
# Create the test_explain combined data if the file does not already exist
if(!file.exists("./data/logistic_test_explain.rds")) {

@@

  # Save the combined test and explain data
  saveRDS(logistic_test_explain, "./data/logistic_test_explain.rds")

@@

  # Load in the data
  logistic_test_explain <- readRDS("./data/logistic_test_explain.rds")

@@

```{r}
# Create the lime comparison data if the file does not already exist
if(!file.exists("./data/logistic_lime_comparisons.rds")) {

@@

  # Save the lime comparison data frame
  saveRDS(logistic_lime_comparisons, "./data/logistic_lime_comparisons.rds")

@@

  # Load in the lime comparison data frame
  logistic_lime_comparisons <- readRDS("./data/logistic_lime_comparisons.rds")

>>>>

  # Save the model
  saveRDS(logistic_mains, "../../../data/logistic_mains.rds")

@@

  # Load the model
  logistic_mains <- readRDS("../../../data/logistic_mains.rds")

@@

```{r}
# Fit or load the logistic regression model with all two way interactions
if(!file.exists("../../../data/logistic_inters2.rds")) {

@@

  # Save the model
  saveRDS(logistic_inters2, "../../../data/logistic_inters2.rds")

@@

  # Load the model
  logistic_inters2 <- readRDS("../../../data/logistic_inters2.rds")

@@

```{r}
# Fit or load the lasso logistic regression model
if(!file.exists("../../../data/logistic_lasso.rds")) {

@@

  # Save the model
  saveRDS(logistic_lasso, "../../../data/logistic_lasso.rds")

@@

  # Load the model
  logistic_lasso <- readRDS("../../../data/logistic_lasso.rds")

@@

```{r}
# Create or load the lime and explain objects for the main effects logisitic regression model
if(!file.exists("../../../data/lime_explain_mains.rds")) {

@@

  # Save the lime and explain objects
  saveRDS(lime_explain_mains, "../../../data/lime_explain_mains.rds")

@@

  # Load the lime and explain objects
  lime_explain_mains <- readRDS("../../../data/lime_explain_mains.rds")

@@

```{r}
# Apply the run_lime function if the lime results file does not already exist
if(!file.exists("../../../data/logistic_lime_inputs.rds")) {

@@

  # Save the lime objects
  saveRDS(logistic_lime_inputs, "../../../data/logistic_lime_inputs.rds")
  saveRDS(logistic_lime, "../../../data/logistic_lime.rds")
  saveRDS(logistic_explain, "../../../data/logistic_explain.rds")

@@

  # Load in the lime objects
  logistic_lime_inputs <- readRDS("../../../data/logistic_lime_inputs.rds")
  logistic_lime <- readRDS("../../../data/logistic_lime.rds")
  logistic_explain <- readRDS("../../../data/logistic_explain.rds")

@@

```{r}
# Create the test_explain combined data if the file does not already exist
if(!file.exists("../../../data/logistic_test_explain.rds")) {

@@

  # Save the combined test and explain data
  saveRDS(logistic_test_explain, "../../../data/logistic_test_explain.rds")

@@

  # Load in the data
  logistic_test_explain <- readRDS("../../../data/logistic_test_explain.rds")

@@

```{r}
# Create the lime comparison data if the file does not already exist
if(!file.exists("../../../data/logistic_lime_comparisons.rds")) {

@@

  # Save the lime comparison data frame
  saveRDS(logistic_lime_comparisons, "../../../data/logistic_lime_comparisons.rds")

@@

  # Load in the lime comparison data frame
  logistic_lime_comparisons <- readRDS("../../../data/logistic_lime_comparisons.rds")

### 2019-08-24 journals/04-assessing_lime/04-assessing_lime.Rmd
updated journals after organization

```{r}
# Load libraries
library(gretchenalbrecht)
#library(seriation)
library(tidyverse)

@@

```{r}
# Fit a random forest model with the top two most important features in the model
if(!file.exists("./data/rfmodel.rds")) {

@@

  # Save the random forest
  saveRDS(rfmodel, "./data/rfmodel.rds")

@@

  # Load the rf model
  rfmodel <- readRDS("./data/rfmodel.rds")
}
```

@@

```{r eval = FALSE}
# Create or load the lime and explain objects for the main effects logisitic regression model
if(!file.exists("./data/lime_explain_sub.rds")) {

@@

  # Save the lime and explain objects
  saveRDS(lime_explain_sub, "./data/lime_explain_sub.rds")

@@

  # Load the lime and explain objects
  lime_explain_sub <- readRDS("./data/lime_explain_sub.rds")

@@

```{r eval = FALSE}
create_bin_df <- function(bin_cut) {
 data.frame(quantile = c("0%", "25%", "50%", "75%", "100%"), 
            bin_cut) 
}

@@

```{r eval = FALSE}
(case1 <- lime_explain_sub$explain %>% filter(case == 1))
```

```{r eval = FALSE}
ggplot() +
  geom_point(data = hamby173and252_train %>% filter(samesource == FALSE),
             aes(x = rough_cor, y = ccf),
             color = "darkgrey",
             alpha = 0.2) +
  geom_point(data = hamby173and252_train %>% filter(samesource == TRUE),
             aes(x = rough_cor, y = ccf),
             color = "darkorange") + 
  geom_vline(xintercept = bin_cuts$rough_cor) + 
  geom_hline(yintercept = bin_cuts$ccf) +
  theme_minimal()
```

```{r eval = FALSE}
ggplot() + 
  geom_point(data = hamby224_test_subset, 
             aes(x = rough_cor, y = ccf, color = rfscore),
             alpha = 0.5) + 
  scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
  geom_point(data = lime_explain_sub$explain %>% 
               filter(case == 1) %>%
               select(feature, feature_value) %>%
               spread(key = feature, value = feature_value),
             aes(x = rough_cor, y = ccf)) +
  geom_vline(xintercept = bin_cuts$rough_cor) + 
  geom_hline(yintercept = bin_cuts$ccf) + 
  theme_minimal()
```

>>>>

```{r}
# Load libraries
library(gretchenalbrecht)
library(lime)
#library(seriation)
library(tidyverse)
library(randomForest)

# Load in the training data 
hamby173and252_train <- read.csv("../../../data/hamby173and252_train.csv")

@@

```{r}
# Fit a random forest model with the top two most important features in the model
if(!file.exists("../../../data/rfmodel.rds")) {

@@

  # Save the random forest
  saveRDS(rfmodel, "../../../data/rfmodel.rds")

@@

  # Load the rf model
  rfmodel <- readRDS("../../../data/rfmodel.rds")
}
```

@@

```{r}
# Create or load the lime and explain objects for the main effects logisitic regression model
if(!file.exists("../../../data/lime_explain_sub.rds")) {

@@

  # Save the lime and explain objects
  saveRDS(lime_explain_sub, "../../../data/lime_explain_sub.rds")

@@

  # Load the lime and explain objects
  lime_explain_sub <- readRDS("../../../data/lime_explain_sub.rds")

@@

```{r}
create_bin_df <- function(bin_cut) {
 data.frame(quantile = c("0%", "25%", "50%", "75%", "100%"), 
            bin_cut) 
}

@@

```{r eval = TRUE}
(case1 <- lime_explain_sub$explain %>% filter(case == 1))
```

```{r eval = TRUE}
ggplot() +
  geom_point(data = hamby173and252_train %>% filter(samesource == FALSE),
             aes(x = rough_cor, y = ccf),
             color = "darkgrey",
             alpha = 0.2) +
  geom_point(data = hamby173and252_train %>% filter(samesource == TRUE),
             aes(x = rough_cor, y = ccf),
             color = "darkorange") + 
  geom_vline(xintercept = bin_cuts$rough_cor) + 
  geom_hline(yintercept = bin_cuts$ccf) +
  theme_minimal()
```

```{r eval = TRUE}
ggplot() + 
  geom_point(data = hamby224_test_subset, 
             aes(x = rough_cor, y = ccf, color = rfscore),
             alpha = 0.5) + 
  scale_color_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
  geom_point(data = lime_explain_sub$explain %>% 
               filter(case == 1) %>%
               select(feature, feature_value) %>%
               spread(key = feature, value = feature_value),
             aes(x = rough_cor, y = ccf)) +
  geom_vline(xintercept = bin_cuts$rough_cor) + 
  geom_hline(yintercept = bin_cuts$ccf) + 
  theme_minimal()
```
